Degrees Draft Syllabus

### 2023-04-06 Bookdown Syllabus/Bookdown Syllabus.Rmd
include code for installing exercises

>>>>

#### **Install the Course's exercises**

Once you've installed R and set up R studio, open R studio, open a new script, and copy and paste the code below to install the exercises that accompany this course.

```{r install_exercises, eval = F}
# Try to install the swirl package
try(install.packages("swirl", repos = "https://cloud.r-project.org/"))

# Uninstall the DegreesNYC_RCourse
try(swirl::uninstall_course("DegreesNYC_RCourse"), silent = T)

# Install the DegreesNYC_RCourse
try(swirl::install_course_github("R-Gilliard-Jr", "DegreesNYC_RCourse", branch = "main"))
```
